Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/COVID-19-Government]

### 2022-04-27 outputs/paper/paper.Rmd
github link updated

---
title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "COVID-19 influences on U.S citizens' mind regarding government actions"
author: 
  - SangWoong Lee
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined to find out U.S citizens' opinions on government budget sectors that were changed by COVID-19. I have found that there existed variables that presented negative, positive and unchanged responses. This is important in a sense that it relates to lives as well as becomes an indication for why such gap exited. We will discuss its importance in details later in discussion session."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/COVID-19-Government]"
subtitle: "COVID-19 influences on U.S citizens' mind regarding government actions"
author: 
  - SangWoong Lee
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "This paper has been examined to find out U.S citizens' opinions on government budget sectors that were changed by COVID-19. I have found that there existed variables that presented negative, positive and unchanged responses. This is important in a sense that it relates to lives as well as becomes an indication for why such gap exited. We will discuss its importance in details later in discussion session."
output:
  bookdown::pdf_document2:
    fig_caption: yes
toc: FALSE
bibliography: references.bib
---
